Concurrent Programming with CXL

### 2020-06-17 book/paper.tex
Latest
Latest version

\chapter{Reader/Writer Lock, Part 2}
\label{ch:rdwr2}

@@

We will discuss ways of preventing deadlock later, but one important
approach to avoiding deadlock is to establish an ordering among the
resources (in this case the forks) and, when needing more than one
resource, always acquiring them in order.  In the case of the philosopers,
they could prevent deadlock by always picking up the lower numbered fork
before the higher numbered fork, like so:

>>>>

\chapter{Reader/Writer Locks, Part 2}
\label{ch:rdwr2}

@@

We will discuss ways of preventing deadlock later (Chapter~\ref{ch:deadlockprevention},
but one important
approach to preventing deadlock is to prevent a cycle from forming, with each
process waiting for the next process on the cycle.
We can do this by establishing an ordering among the
resources (in this case the forks) and, when needing more than one
resource, always acquiring them in order.  In the case of the philosopers,
they could prevent deadlock by always picking up the lower numbered fork
before the higher numbered fork, like so:
